### 2019-09-25 README.Rmd
added talking points about graphics group
updated notes after meeting

- Sometimes LIME does not want to run in R

```{r error = TRUE, message = FALSE}
library(caret)
library(lime)

# Split up the data set
iris_test <- iris[1:5, 1:4]
iris_train <- iris[-(1:5), 1:4]
iris_lab <- iris[[5]][-(1:5)]

# Create Random Forest model on iris data
model <- train(iris_train, iris_lab, method = 'rf')

# Create an explainer object
explainer <- lime(iris_train, model)

# Explain new observation
explanation <- explain(iris_test, explainer, n_labels = 1, n_features = 2)
```

@@

*First draft of paper due Wednesday, September 18)*

>>>>

**LIME**

- What names should I give to the diagnostic plots?
- Color themes for the paper?
- Metrics:
    - MSEE (mean squared explanation error?) versus locality metric which would need to be computed via the perturbations
    - Do we want to think of a metric that is stand alone? - not just for comparisons

@@
